\article{Introduction}

\asection{Name}
\begin{enumerate}
	\item The name of this student-ran organization shall be: “Benjamin Franklin
		High School Open”.

	\item It should be abbreviated: “BFHS-Open”.

	\item It conducts business as the “Benjamin Franklin High School Computer Science
		Club”.
\end{enumerate}

\asection{Purpose}
\begin{enumerate}
	\item The purpose of this organization is to support and foster computer scientists
		and open source software in the community surrounding Benjamin Franklin High
		School.

	\item All choices will be for the betterment of the students at Benjamin Franklin
		High School.
\end{enumerate}

\asection{Objectives} The objectives of BFHS-Open are:
\begin{enumerate}
	\item Cultivate open forms of collaboration between students at Benjamin Franklin
		High School.

	\item To maintain a common space, digital and otherwise, that is inclusive and
		accepting to all people.

	\item To develop and present resources for education relevant to it's purpose.

	\item To enable the self-determination of it's members.
\end{enumerate}

\asection{Ideals}
\begin{enumerate}
	\item Openness as derived from the open movement - for the goal of reducing friction
		in the sharing of information.

	\item Freedom, defined both in terms of beer and in speech.

	\item Inclusivity for all members.

	\item Supporting the education of one’s peers.
\end{enumerate}

\asection{Approach}
\begin{enumerate}
	\item Authentic Discourse as a means for generating change, inward and outward
		facing.

	\item Educating students and community members in digital topics.

	\item Providing utilities, services, and lessons on software and computers to peers.
\end{enumerate}