\article{Involvement}

\asection{General Membership}
\begin{enumerate}
	\item Requirements for General Membership is as follows:
		\begin{enumerate}
			\item Actively enrolled at Benjamin Franklin High School.

			\item Attend 1 in-person meeting.
		\end{enumerate}

	\item General Membership grants:
		\begin{enumerate}
			\item All benefits afforded to members of the Organization.

			\item Access to during-school, after-school, and out-of-school activities.

			\item Access to private members-only Organization events.
		\end{enumerate}

	\item If one fulfills all requirements listed, they are registered as a member
		for the duration of the academic year.
\end{enumerate}

\asection{Active Membership}
\begin{enumerate}
	\item Requirements for Active Membership is as follows:
		\begin{enumerate}
			\item General Membership or equivalent Probational Membership (\refsection{Probationary Membership})..

			\item Participate in at least 4 in-person meetings.
		\end{enumerate}

	\item Active Membership grants:
		\begin{enumerate}
			\item Ability to vote in General (\refsection{General Election}) and Snap
				Elections (\refsection{Snap Election}).

			\item Right to run for Executive Board positions (\refarticle{Executive Board}).
			
			\item Access to the Organization's Version Control systems.
		\end{enumerate}

	\item Once all requirements are met, the Individual will be grated an Active
		Membership for the duration of the Academic Year, with an optional 4-week Probational
		Active Membership at the start of a new Academic Year.
\end{enumerate}

\asection{Probationary Membership}
\begin{enumerate}
	\item Requirements for Probationary Membership is as follows:
		\begin{enumerate}
			\item Placeholder due to forced ceasing of participation due to Failure to
				Meet Requirements (\refsection{Failure to Meet Requirements}).

			\item Placeholder due to start of new Academic Year.
		\end{enumerate}

	\item Probationary Membership grants:
		\begin{enumerate}
			\item All rights accompanied to that of the equivalent Non-Probationary Membership.
		\end{enumerate}

	\item Probationary Membership lasts until the set period ends.
		\begin{enumerate}
			\item If the Individual re-registers for their previous Membership, the
				Individual will be granted said position and their Probationary
				Membership will be revoked.

			\item If the Individual fails to re-register for their previous Membership,
				their Probationary Membership will be removed and their will lose the
				ability to re-register for their position.
		\end{enumerate}
\end{enumerate}

\asection{Contributing Membership}
\begin{enumerate}
	\item Requirements for Contributing Membership is as follows:
		\begin{enumerate}
			\item Active Membership or equivalent Probational Membership (\refsection{Probationary Membership}).

			\item Either:
				\begin{enumerate}
					\item Presented and aided in the educational activities of the Organization.

					\item Contributed to the open-source activities of the Organization.
				\end{enumerate}

			\item Approved by Executive Committee.
		\end{enumerate}

	\item Contributing Membership grants:
		\begin{enumerate}
			\item Better access to the planning and operation of activities of the Organization.

			\item Trusted committing status to all Organization repositories.
		\end{enumerate}

	\item Once all requirements are met, the Individual will be grated an
		Contributing Membership for the duration of the Academic Year

	\item Contributing Membership is accompanied by an optional 4-week Probational
		Contributing Membership at the start of the next Academic Year.

	\item A Contributor Member must give 24 hours notice before resigning.
\end{enumerate}

\asection{Executive Membership}
\begin{enumerate}
	\item Requirements for Executive Membership is as follows:
		\begin{enumerate}
			\item Active Membership.

			\item Elected to specific Board Position (\refarticle{Executive Board}).

			\item Elected in General Election (\refsection{General Election}).
		\end{enumerate}

	\item Executive Membership grants:
		\begin{enumerate}
			\item Position on Executive Committee.

			\item Specialized privileges listed in the appropriate section of (\refsection{Executive Board}).
		\end{enumerate}

	\item Once all requirements are met, the Individual will be granted an
		Executive Membership and it's accompanying Executive Board position for the
		duration of the Academic Year

	\item Executive Membership is accompanied by an optional 4-week Probational Membership,
		equivalent to their previous Non-Executive Membership, at the start of the Academic
		Year.

	\item An Executive Member must give 72 hours notice before resigning, and the
		replacement will be chosen as designated by their job title (\refarticle{Executive Board}).
\end{enumerate}

\asection{Sponsor}
\begin{enumerate}
	\item Requirements for Sponsor is as follows:
		\begin{enumerate}
			\item Approved by Benjamin Franklin High School.
		\end{enumerate}

	\item They gain the following privileges:
		\begin{enumerate}
			\item Approving and certifying elections (\refsection{Voting Method}).

			\item Approving of Impeachment (\refsection{Impeachment}).

			\item Enforcing of expulsions (\refsection{Expulsion}).

			\item Control of organization assets and holdings (\refarticle{Financial Structure}).
		\end{enumerate}

	\item If one fulfills all requirements listed, they are registered as the
		organizational sponsor and will hold their position until stepping down.
\end{enumerate}