\article{Executive Board}

\asection{President}
\begin{enumerate}
	\item Elected by Active Members.

	\item The duties of the President is as follows:
		\begin{enumerate}
			\item Supervise all (or send appropriate alternative member to) Organization
				events and activities.

			\item Preside over the Executive Committee.
		\end{enumerate}

	\item The president is the face and leader of the Executive Board.

	\item If the President is impeached or resigns, the Vice President will become
		the new President, with a new Snap Election (\refsection{Snap Election})
		being held to elect a new Vice President.
\end{enumerate}

\asection{Vice President}
\begin{enumerate}
	\item Elected by Active Members.

	\item The duties of the Vice President is as follows:
		\begin{enumerate}
			\item Managing of promotions and demotions in relation to Membership (\refarticle{Involvement}).

			\item Support the President in their duties.
		\end{enumerate}

	\item If the Vice President is impeached or resigns, the Executive Board will
		elect a new member as a replacement.
\end{enumerate}

\asection{Secretary}
\begin{enumerate}
	\item Elected by Active Members.

	\item The duties of the Secretary is as follows:
		\begin{enumerate}
			\item Communication between Executive Board and the Organization's Members.

			\item Logging the activity of Individual Members.

			\item Publishing of Organization materials.

			\item Management and preparation of Organization events and activities.
		\end{enumerate}

	\item If the Secretary is impeached or resigns, the Executive Board will elect
		a new member as a replacement.
\end{enumerate}

\asection{Outreach Director}
\begin{enumerate}
	\item Elected by Active Members.

	\item The duties of the Outreach Director is as follows:
		\begin{enumerate}
			\item Communication between the Organization and outside groups and organizations.

			\item Management of Organization social media accounts and platforms.
		\end{enumerate}

	\item If the Outreach Director is impeached or resigns, the Executive Board
		will elect a new member as a replacement.
\end{enumerate}

\asection{Tech Lead}
\begin{enumerate}
	\item Elected by Active Members.

	\item The duties of the Tech Lead is as follows:
		\begin{enumerate}
			\item Management of Organization Technology.

			\item Operation of Organization source-control systems.
		\end{enumerate}

	\item If the Tech Lead is impeached or resigns, the Executive Board will elect
		a new member as a replacement.
\end{enumerate}
